Solar wind predictions for the Parker Solar Probe orbit

### 2017-10-18 paperMVVB_referee/referee_report_responses.txt

Referee Report

This paper discusses a method of using OMNI and Helios solar wind data to estimate the solar wind parameters that might be expected during the upcoming Parker Solar Probe mission. It includes an estimate of how these parameters might vary with solar cycle, though this is a relatively small correction, and the likely sunspot number during the mission is anyway highly uncertain. The analysis appears to be thorough, retaining information on the log-normal distribution of the parameters that is used to produce “model” representations of the distributions and their variation during the solar cycle. However, in the end, this information isn’t used in the predictions at PSP, where only median values are considered. It’s also not clear whether this type of analysis has any advantage over say a simple-minded approach where you use the radial dependence of averaged Helios values to propagate averaged 1 AU values, perhaps taken at different times in the solar cycle, down to the PSP orbit. My suspicion is that the results might not be all that different, but the authors might like to address this point. The extrapolated values do appear to be fairly consistent with previous estimates of near Sun parameters, and deviations, e.g. in the speed profile can be plausibly accounted for, so the results appear to be reasonable.

- added a new figure in end of section 6: figure 14 shows the predicted solar wind distributions at the first and closest perihelia
+ use the distributions for the predictions (add perihelia figures of distributions)

- true, the results would not be that different. We stated that in the discussion section and explained the advantage of our method
+ state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)

@@

- adopted
+ highlighted
+ can be adopted

Next paragraph, last sentence, suggest: the perihelion distance to be reduced to a minimum of 9.86 Rs. Reverse figures 10 and 11, since figure 11 is referenced first, or just remove the mention of Figure 11 here, which isn't necessary; the statement can be understood without looking at the figure.

- adopted
+ highlighted
+ can be adopted

- switched order of figures 10 and 11
- added 'top' and 'bottom' pointers to both references of now figure 10 and added the time when the closest perihelion will occur at the first figure reference
+ highlighted
+ manage fig references

@@

- integrated list item about slow/fast wind balance into velocity list item

Page 23, last but one paragraph: Again, there are points here that have already been said twice above.

- removed paragraph
+ highlighted
+ remove or merge with above

- other changes:
- added referee acknowledgment
- We found mismatching density values and corrected a typo in our density calculation. The error affected the densities for the first and nearest perihelia and the curves for density in figures 12 and 13. (abstract, section 6 and summary: corrected values 4015 to 214 and 9733 to 2951 cm-3)
- caption figure 13: removed a duplicate 'during'; replaced nearest with first closest

### 2017-10-18 paperMVVB/sections/abstract.tex
text to figure 14; difference to simple-minded approach; made changes bold face

\abstract
{The Parker Solar Probe (PSP) (formerly Solar Probe Plus) mission will be humanity’s first in situ exploration of the solar corona with closest perihelia at \num{9.86}~solar radii (\si{\Rs}) distance to the Sun. It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles. The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years \numrange{2018}{2025}. The study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data. The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au} over more than five solar cycles. The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.}	%aims
{The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions. In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part. Functional relations to solar activity are compiled with use of the OMNI data by correlating and fitting the frequency distributions with the SSN. Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies. Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions. Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
{The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance. The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}. The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}. \textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned. } }	%results
{}	%conclusions

>>>>

\abstract
{The Parker Solar Probe (PSP) (formerly Solar Probe Plus) mission will be humanity’s first in situ exploration of the solar corona with closest perihelia at \num{9.86}~solar radii (\si{\Rs}) distance to the Sun. It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles. The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years \numrange{2018}{2025}. The study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data. The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au} over more than five solar cycles. The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.}	%aims
{The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions. In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part. Functional relations to solar activity are compiled with use of the OMNI data by correlating and fitting the frequency distributions with the SSN. Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies. Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions. Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
{The CGAUSS empirical solar wind model for PSP yields dependencies \textbf{on solar activity and solar distance for the solar wind parameters' frequency distributions}. The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}. The estimates for PSP’s \textbf{first closest perihelion, occuring} in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}. \textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned. } }	%results
{}	%conclusions

### 2017-10-18 paperMVVB/sections/content.tex
text to figure 14; difference to simple-minded approach; made changes bold face

For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$). Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c'$ and for the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.

@@

%\subsection{Near-Sun extrapolation for PSP orbit}
%PSP orbit
Parker Solar Probe is planned to launch in mid 2018. With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}. Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \textbf{the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
	\caption{PSP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
\end{figure}

@@

%\subsection{PSP solar wind environment estimation}
Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected. Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_f_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's \textbf{closest} perihelion at \SI{0.0459}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
\end{figure}
\textbf{Monthly SSNs---shifted by the time lags specific to the solar wind parameters---are used in the calculation of the solar wind predictions. These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties. The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.} In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
%B
% 87.3642361846083
%N
% 213.613795298952	first
% 2950.67837375615	nearest
% 2925.63248639046	SSN 0
% 3421.59065204775	SSN 200
%T
% 503136.759398494

(see Fig.~\ref{fig:SPP_sw_distributions})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
	\caption{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those extrapolated to PSP's first and closest perihelia.}
	\label{fig:SPP_sw_distributions}
\end{figure}

@@

\textbf{For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by \textbf{deriving lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature. Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution. Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges. The OMNI multi-spacecraft solar wind data is intercalibrated and covers almost five solar cycles. It thus represents solar wind gathered at different phases of solar activity in the ecliptic plane. In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN. The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database. Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP. The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.

However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}. \textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements of the other studies. This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}). The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is believed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).

@@

%\section{Summary}
%\label{sec:summary}
With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
\begin{itemize}
	\item The dependency of the magnetic field strength median value \textbf{(\ref{eq:median_B})} on solar activity and radial \textbf{distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
	\item The estimated magnetic field strength median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements. The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}. Thus, at solar minimum with sunspot number around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and dropping to \SI{28}{\%} during solar maximum conditions with sunspot numbers around 200.
	\item The calculated median velocity values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
	\item The median proton density \textbf{relation (\ref{eq:median_n}) seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
	\item The estimated density values for PSP's first and closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
	\item The derived correlation function for the median proton \textbf{temperature (\ref{eq:median_T}) seems} to provide too high temperature values \textbf{around PSP’s perihelion} in comparison to coronal measurements.
	\item The estimated temperature values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
\end{itemize}

>>>>

For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters $d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$. Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c'$ and for the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.

@@

%\subsection{Near-Sun extrapolation for PSP orbit}
%PSP orbit
Parker Solar Probe is planned to launch in mid 2018. With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}. Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs}\textbf{. This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015} as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
	\caption{PSP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
\end{figure}

@@

%\subsection{PSP solar wind environment estimation}
Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, \textbf{we can infer} which solar wind parameter magnitudes can be expected. Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show \textbf{the median values (\ref{eq:median_with_ssn}) of} the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the \textbf{first} closest perihelion in December 2024.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_f_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) \textbf{during} 12~days in 2024 with PSP's \textbf{22nd (the first closest)} perihelion at \SI{0.0459}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
\end{figure}
In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the \textbf{first} closest approach at \SI{0.046}{\au}. \textbf{Monthly SSNs---shifted by the time lags specific to the solar wind parameters---are used in the calculation of the solar wind predictions. These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties. The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.}
%B
% 87.3642361846083
%N
% 213.613795298952	first
% 2950.67837375615	nearest
% 2925.63248639046	SSN 0
% 3421.59065204775	SSN 200
%T
% 503136.759398494

\textbf{Now the estimated solar wind environment can finally be derived from the function $W'''(x,ssn,r)$. The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions}.}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelia. In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}}
	\label{fig:SPP_sw_distributions}
\end{figure}
\textbf{Note again that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual by PSP to be encountered values are expected to be smaller.}

@@

\textbf{For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by \textbf{deriving lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature. Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution. Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges. The OMNI multi-spacecraft solar wind data is intercalibrated and covers almost five solar cycles. It thus represents solar wind gathered at different phases of solar activity in the ecliptic plane. In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN. The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.

\textbf{For determining solar activity and solar distance dependent relations exclusively for the median and average solar wind values, we would have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data---scaled with the SSN. The results of this simpler analysis method would be similar (at least the distance scaling results are similar; compare the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}) and would be sufficient for this purpose. Though, we are not only interested in the averages but in the bulk distributions, that is, the whole range of values which might occur. For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions. With our approach we are able to control and fit this distance.}

\textbf{It} is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP. The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks. However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}. \textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements of the other studies. This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}). The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is believed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).

@@

%\section{Summary}
%\label{sec:summary}
With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
\begin{itemize}
	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
	\item The estimated magnetic field strength \textbf{median values (\ref{eq:median_B})} for PSP's first and \textbf{first} closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements. The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}. Thus, at solar minimum with \textbf{a SSN} around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and \textbf{drops} to \SI{28}{\%} during solar maximum conditions with \textbf{a SSN} around 200.
	\item The calculated median velocity values for PSP's first and \textbf{first} closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
	\item The \textbf{proton density relation seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
	\item The estimated density \textbf{median values (\ref{eq:median_n})} for PSP's first and \textbf{first} closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
	\item The derived correlation function for the \textbf{proton temperature seems} to provide too high temperature values \textbf{around PSP’s closest perihelion} in comparison to coronal measurements.
	\item The estimated temperature \textbf{median values (\ref{eq:median_T})} for PSP's first and \textbf{first} closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
\end{itemize}
